Watch Out for the Bully! Study of Interference Between Jobs Running Concurrently on Dragonfly Network

### 2016-03-09 draft.tex
update figures in section 4

@@

\section{Dragonfly Network}
\label{sec:network}
It is difficult to do experiment with concurrently running jobs on HPC system. One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will. Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results. Therefore, we resort to simulation in our work.

A simulation toolkit named CODES enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.  CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}. It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.

\subsection{Network Configuration}
\label{sec: network config}

Here will talk about network configuration, such as network scale, link bandwidth etc.\\

@@

Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution. There are many works study various ways of doing job placement on HPC systems with different topologies \cite{yang-cluster14} \cite{zhou-ipdps15} \cite{hoefler-hpdc14}. In this work, we study the following two placement schemes:

@@

\section{Evaluation}
\label{sec:evaluation}

\subsection{Application}
\label{sec:app study}

@@

AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages. It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}.

MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}. It is widely used for structured grid physics packages.

CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos.

\subsection{Workload Overview}
\label{sec: workload overview}

@@

\subsection{Analysis of Synthetic Workloads}

>>>>

\makeatletter % Put Roman Number in Text
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

@@

\section{Background}
\label{sec:background}
The dragonfly network is promising alternative for connecting a large number of nodes for its high-radix and low-diameter topology\cite{dally-dragonfly} \cite{kim-micro} \cite{faanes}. However, even with such powerful network, the job placement and routing could still be important factor that impact application's performance.

\subsection{Dragonfly Network Overview}
\label{sec:network}
The dragonfly is a two-level hierarchical topology. It consists of several groups connected by All-to-All links. In each group, there could be ``a" number of routers connected via All-to-All local channels. For each router, there could be ``p" number of compute nodes attached to it via terminal link. The router has ``h" number of global channels that used as intergroup connections through which the router connected to other router in different groups. Thus, the radix of each router is $k = a+h+p-1$. The implementation of such dragonfly network could be different between different computing facilities. The choosing of proper $a$, $h$, $p$ could be involving many factors, such as system scale, building cost and workload requirements.

For the purpose of loading balance, it is recommended that the proper dragonfly configuration is $a=2p=2h$\cite{kim-micro}. Under this configuration, the total number of groups ``g" in the dragonfly network would be $g = a*h+1 $, the total number of compute nodes ``N" in the network would be $N = p*a*g = $.

@@

Job placement refers to the scheme used by batch scheduler to allocate the required number of nodes by the job for execution. As studied by several researchers, the job placement could be an important factor that impact application performance \cite{hoefler-hpdc14} \cite{bhatele-sc11} \cite{jain-sc14}. In this work, we study the following two placement schemes:

@@

\section{Methodology}
\label{sec: methodology}

It is difficult to do experiment with concurrently running jobs on HPC system. One reason is that job placement and routing strategy are part of system configuration, it is impossible for user to make changes at will. Another reason is that it is unrealistic to reserve the system exclusively to run the same batch of jobs with desired placement and routing configurations and compare the results. Therefore, we resort to simulation in our work.

\subsection{Simulation Tool}
A simulation toolkit named CODES, Co-Design of Multilayer Exascale Storage Architectures, enables the exploration of simulating different HPC networks with high fidelity and great scalability\cite{codes}.  CODES support dragonfly network with high fidelity flit-level simulation\cite{codes-dragonfly}. It has this network workload component that is capable of taking real MPI application traces generated by SST DUMPI\cite{sst} for trace-driven simulations.

\subsection{Application Traces}
\label{sec: application traces}

@@

AMG: The Algebraic MultiGrid Solver, is a parallel algebraic multi-grid solver for linear systems arising from problems on unstructured mesh physics packages. It has been derived directly from the BoomerAMG solver that is being developed in the Center for Applied Scientific Computing (CASC) at LLNL\cite{amg}. The traces of AMG we chosen are comprised of 216 MPI ranks.

MultiGrid: massively parallel block-structured adaptive mesh refinement (AMR) codes a software framework for massively parallel block-structured adaptive mesh refinement (AMR) codes\cite{boxlib}. It is widely used for structured grid physics packages. The traces of AMG we chosen are comprised of 125 MPI ranks.

CrystalRouter: the extracted communication kernel of the full application Nek5000\cite{nek5000}, which is a spectral element CFD application developed at Argonne National Laboratory\cite{crystalrouter}. It features spectral element multi-grid solvers coupled with a highly scalable, parallel coarse-grid solver that is widely used for projects including ocean current modeling, thermal hydraulics of reactor cores,and spatiotemporal chaos. The traces of AMG we chosen are comprised of 100 MPI ranks.

\subsection{Simulation Configuration}
\label{sec: simulation configuration}

The dragonfly network studied in this work consists of 33 groups, each group contains 8 routers and each router has 4 compute nodes attached to it. Overall, there are 264 routers and 1056 compute nodes in the network. The bandwidth of both terminal links and local channel are set to 2GB/s, the global channel bandwidth is set to 4GB/s.

There are four placement and routing scheme combinations, namely contiguous placement coupled with minimal routing, contiguous placement coupled with adaptive routing, random placement coupled with minimal routing, random placement coupled with adaptive routing.  In this work, we enable the applications running on dragonfly network under different placement and routing scheme combination, and scrutinize the application's performance and network behavior in different running scenarios.

\section{Parallel Workload \Rmnum{1 } Study}
\label{sec: workload 1 overview}

@@

\section{Parallel Workload \Rmnum{2 } Study}
